Verifying Demonstrations

### 2018-11-27 paper/adversary-model.tex
Clarifies adversary model
Adapts the adversary to "not make things worse"
We want to see if we make things worse, thus we don't consider the
deanonymizing witness since in that situation the adversary can identify
and arrest all participants anyway.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the base adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time it happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\) (from \cref{base-adversary}).
  }
\end{figure}

\begin{adversaries}
\item\label{base-adversary}
  \emph{Base adversary}:
  The adversary maliciously controls \(W\).
  The adversary honest-but-curiously controls \(S\).
  The adversary only learns the protocol data --- \ie what is sent over the 
  channel, no auxiliary data (such as who sent it).

\item\label{deanonymizing-witness-adversary}
  \emph{Deanonymizing-witness adversary}:
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  %(\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still learns only the protocol data, no auxiliary data.

\item\label{deanonymizing-adversary}
  \emph{Fully deanonymizing adversary}:
  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
\end{adversaries}

The base adversary (\cref{base-adversary}) represents an adversary that has no 
access to auxiliary information, \eg inferences that can be done from the 
communication layer, which means that it has only the protocol data at its 
disposal.

We find \cref{base-adversary} suitable when the protester and witness both move 
in a crowd and there is no way for the witness to decide exactly with whom he 
or she communicates with.
However, in some situations this might not be the case: \Eg if the crowd is not 
dense the witness will likely see the face of the protester.
If the witness is controlled by the adversary, then it is likely that the 
witness can capture a picture of the face, which can be turned into an identity 
through face recognition.
There are various such scenarios leading to the adversary learning the 
protester's identity, we capture this as 
\cref{deanonymizing-witness-adversary}.

As to \(S\), \cref{base-adversary} corresponds to an adversary who cannot 
control the channel between \(P\) and \(S\), \eg when \(P\) uses 
Tor~\cite{Tor}.
The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
\(S\) learns it, \eg when \(S\) is operated outside the adversary's 
jurisdiction.

However, given a strong enough adversary, such anonymous communication might 
not be possible; \eg if the adversary can do a time-correlation attack.
We capture such a strong adversary as \cref{deanonymizing-adversary}.

>>>>

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the base adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time it happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\) (from \cref{in-system-adversary}).
  }
\end{figure}

\begin{adversaries}
\item\label{in-system-adversary}
  \emph{In-system adversary}:
  The adversary maliciously controls \(W\).
  The adversary honest-but-curiously controls \(S\).
  The adversary only learns the protocol data --- \ie what is sent over the 
  channel, no auxiliary data\footnote{%
    By auxiliary data we mean any data outside of the protocol.
    \Eg meta-data such as who is on the other side of the channel.
  }

\item\label{deanonymizing-storage-adversary}
  \emph{National eavesdropping adversary}:
  The situation is the same as in \cref{in-system-adversary}, but now the storage 
  \(S\) learns the protester \(P\)'s identity from an auxiliary channel.
  However, \(W\) still learns only the protocol data, no auxiliary data.

%\item\label{deanonymizing-witness-adversary}
%  \emph{Deanonymizing-witness adversary}:
%  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
%  that now \(W\) also learns \(P\)'s identity from an auxiliary channel.
\end{adversaries}

The in-system adversary (\cref{in-system-adversary}) represents an adversary 
that has no access to data from outside the system, \eg inferences that can be 
done from the communication layer (\eg IP-addresses mapped to physical 
identities), which means that it has only the protocol data at its disposal.

We find \cref{in-system-adversary} suitable when the protester and witness both 
move in a crowd and there is no way for the witness to decide exactly with whom 
he or she communicates with.
(The protesters could also simply wear masks.)
We consider this a fair model for our purposes: if the adversary can 
deanonymize the protesters \emph{at the physical location} and thus arrest 
them, the adversary can do that independently of whether the protesters use our 
protocol or not --- thus our protocol cannot make things worse in such a 
situation.

As to \(S\), \cref{in-system-adversary} corresponds to an adversary who cannot 
even observe the channel between \(P\) and \(S\), \eg when \(P\) uses tools 
such as Tor~\cite{Tor}.
The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
\(S\) learns it; \eg \(S\) is operated outside the adversary's jurisdiction and 
so the adversary cannot control \(S\), but since \(S\) provides public access 
the adversary can (possibly constantly) query it and learn things with little 
delay.
However, it might not be realistic to assume that the channel between \(P\) and 
\(S\) is unobservable for the adversary.
\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
thus perform time-correlation attacks on messages on the network and events 
observed through \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(S\) learns 
the identity of the protester.

%However, in some situations this might not be the case: \Eg if the crowd is not 
%dense the witness will likely see the face of the protester.
%If the witness is controlled by the adversary, then it is likely that the 
%witness can capture a picture of the face, which can be turned into an identity 
%through face recognition.
%There are various such scenarios leading to the adversary learning the 
%protester's identity, we capture this as 
%\cref{deanonymizing-witness-adversary}.
